---
title: "Prediction of A Diamond Price"
author: "Ula Jiang"
date: "16 May 2018"
output: ioslides_presentation
---


## Executive Summary

- This project introduces a prediction data product. The dataset is "diamond" from "UsingR" package, with 48 observations about the carat of each diamond and its related price.  
- This project shows the relationship between the carat of a diamond and its price.


## Functionality

1. Make a plot of the 48 observations in the dataset, and then find a linear regression model between the price and carat of a diamond.  
2. Plot the fitted line to show the prediction of the price of a diamond with an unseen carat.

## Detailed Data in "diamond" Dataset
The data in "diamond" dataset is shown as below. We can see there are only two colunms: carat and price. 
```{r, include=FALSE}
library(UsingR)
data("diamond")
```
```{r, echo=TRUE, comment=""}
head(diamond)
```

## Plot Observed Data and Fitted Line

```{r, echo=FALSE, fig.align='center'}
model <- lm(price ~ carat, data = diamond)
plot(diamond$carat, diamond$price, 
         xlab = "Carat of a Diamond",
         ylab = "Price (in dollar $)", 
         xlim = c(0.10, 0.40),
         ylim = c(100, 1250))
abline(model, col = "red", lwd = 2)
```

